RadLib: a radiative heat transfer model library for CFD

### 2020-12-30 manuscript/manuscript.tex
minor edits

Cost comparisons were also attempted with Python, but it is difficult to get meaningful results when mixing Python and C++. In particular, the cost of a single evaluation of the gas properties is small end valuating the gas properties in a Python loop results in the loop appearing to dominate the computational cost. Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Fig.~\ref{f:cost} the cost only varied by about 4\%. The cost of the WSGG model was 0.6~s, which is 7.6 times slower than the C++ version. It is possible that improvements in the Python speed are possible by further optimization of the Cython interface, but the Python radiative solver used in the examples is only meant to demonstrate the use of the library evaluation of gas properties.

>>>>

Cost comparisons were also attempted with Python, but it is difficult to get meaningful results when mixing Python and C++. In particular, the cost of a single evaluation of the gas properties is small and evaluating the gas properties in a Python loop results in the loop appearing to dominate the computational cost. Comparison between Python and C++ for Example S3 is somewhat more meaningful, but even here, for the six cases considered in Fig.~\ref{f:cost} the cost only varied by about 4\%, indicating that the costs are dominated by the Python and not by the model calculations themselves. The cost of the WSGG model was 0.6~s, which is 7.6 times slower than the C++ version. It is possible that improvements to the Python speed could be made by further optimization of the Cython interface, but the Python radiative solver used in the examples is only meant to demonstrate the use of the library evaluation of gas properties.
